%iffalse
\let\negmedspace\undefined
\let\negthickspace\undefined
\documentclass[journal,12pt,onecolumn]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{algorithmic}
\usepackage{multicol}
\usepackage{circuitikz}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{txfonts}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{gensymb}
\usepackage{comment}
\usepackage[breaklinks=true]{hyperref}
\usepackage{tkz-euclide} 
\usepackage{listings}
\usepackage{gvv} 
\usepackage{tikz}
\usetikzlibrary{shapes,arrows} 

%\def\inputGnumericTable{}                                
\usepackage[latin1]{inputenc}                                
\usepackage{color}                                            
\usepackage{array}                                            
\usepackage{longtable}                                       
\usepackage{calc}                                             
\usepackage{multirow}                                         
\usepackage{hhline}                                           
\usepackage{ifthen}                                           
\usepackage{lscape}
\usepackage{tabularx}
\usepackage{array}
\usepackage{float}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{problem}{Problem}
\newtheorem{proposition}{Proposition}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{example}{Example}[section]
\newtheorem{definition}[problem]{Definition}
\newcommand{\BEQA}{\begin{eqnarray}}
\newcommand{\EEQA}{\end{eqnarray}}
\newcommand{\define}{\stackrel{\triangle}{=}}
\theoremstyle{remark}


% Marks the beginning of the document
\begin{document}
\bibliographystyle{IEEEtran}
\vspace{3cm}

\title{\textbf{2018-EE-53-65}}
\author{AI24BTEC11027 - R Sumanth}
\maketitle
\bigskip

\renewcommand{\thefigure}{\theenumi}
\renewcommand{\thetable}{\theenumi}
\setlength{\columnsep}{2.5em}
\begin{enumerate}

\item Let $f(x)=3X^3-7x^2+5x+6.$ The maximum value of $f(x)$ over the interval $\sbrak{0,2}$ is $\underline{\hspace{2cm}}$ (up to $1$ decimal place).\\

\item Let $A=\myvec{1 & 0 & -1\\ -1 & 2 & 0\\ 0 & 0 & -2}$ and $B=A^3-A^2-4A+5I$, where I is the $3\times3$ identity determinant of $B$ is $\underline{\hspace{2cm}}$ (up to $1$ decimal place).\\

\item The capacitance of an air-filled parallel-plate capacitor is $60 pF.$ When a dielectric slab whose thickness is half the distance between the plates, is placed on one of the plates covering it entirely, the capacitance becomes $86 pF.$ Neglecting the fringing effects, the relative permittivity of the dielectric is $\underline{\hspace{2cm}}$  (up to $2$ decimal place).\\ 

\item The unit step response $y(t)$ of a unity feedback system with open loop transfer function $G(s)H(s)=\frac{K}{(s+1)^2(s+2)}$ is shown in the figure. The value of $k$ is $\underline{\hspace{2cm}}$  (up to $2$ decimal place).

\input{circuit/circuit1}

\item A three-phased load is connected to a three-phase balanced supply as shown in the figure. If $v_{an}=100 \angle{0}\degree V,b_{bn}=100\angle{-120}\degree V$ and $V_{cn}=100\angle{-240}\degree V$ (angle are considered positive in the anti-clockwise direction), the value of $R$ for zero current in the neutral wire is $\underline{\hspace{2cm}}\Omega$ (up to $2$ decimal places).\\
\input{circuit/circuit2}

\item The voltage across the circuit in the figure, and the current through it, are given by the following expressions: \\
$v(t)=5-10 \cos{\omega t+60\degree}V$\\
$i(t)=5+X \cos{\omega t}A$\\
where $\omega=100\pi$ radian/s. If the average power delivered to the circuit is zero, then the value of X (in Ampere) if $\underline{\hspace{2cm}}$  (up to $2$ decimal place).\\
\input{circuit/circuit3}

\item A phase controlled single rectifier, supplied by an AC source, feeds power to an R-L-E load as shown in the figure. The rectifier output  voltage has an average value gven by$v_0=\frac{v_m}{2\pi}(3+\cos{\alpha})$, where $v_m=80\pi$ volts and $\alpha$ is the firing angle. If the power delivered to the lossless battery is $1600 W, \alpha$ in degree is $\underline{\hspace{2cm}}$  (up to $2$ decimal place).\\
\input{circuit/circuit4}

\item The load resistance is $1 \Omega.$ The capacitor voltage has negligible ripple. Both converters operate in the continuous conduction mode. The switching frequency is $1 kHz$, and the switch control signals arc as shown. The circuit operates in the steady state. Assuming that the converters share the load equally, the average value $i_S1$ , the current of switch $S1$ (in Ampere), is $\underline{\hspace{2cm}}$  (up to $2$ decimal place).\\
\input{circuit/circuit5}

\item A $3$-phase $900$ kVA, $3$ $kV / \sqrt{3} $k V $(\Delta/Y)$ $50$ Hz transformer has primary (high voltage side) resistance per phase of $0.3 \Omega$ and secondary (low voltage side ) resistance per phase of $0.02 \Omega$. Iron loss of the transformer is $10$ kW. The full load \% efficiency of the transformer operated at unity power factor is $\underline{\hspace{2cm}}$  (up to $2$ decimal place).\\

\item A $200$ V DC series motor, when operating from voltage while driving a certain load, draws $10 A$ current and runs $1000$ r.p.m. The total series resistance is $1 \Omega$. The magnetic circuit is assumed to be linear. At the same voltage, the load torque is increased by $44\%$. The speed of the motor in r.p.m. (rounded to the nearest integer) is $\underline{\hspace{2cm}}$ \\

\item A dc to dc converter shown in the figure is charging a batery bank, B$2$ whose voltage is constant at $150$ V. B$1$ is another battery bank whose voltage is constant at $50$ V. The value of the inductor, L is $5$mH and the ideal switch, S is operated with a switching frequency of $5$ kHz with a duty ratio of $0.4.$ Once the circuit has attained steady state and assuming the diode D to be ideal, The power transferred from B$1$ to B$2$
(in watt) is $\underline{\hspace{2cm}}$  (up to $2$ decimal place).\\
\input{circuit/circuit6}

\item The equivalent circuit of a single phase induction motor is sown in the figure, where the parameters are $R_1=R_2^1=X_{l1}^1=X_{l2}^1=12\Omega, X_M=240\Omega$ and $S$ is the slip. At no-load, the motor speed can be approximated to be the synchronous speed. The no-load lagging power factor of the motor is $\underline{\hspace{2cm}}$  (up to $3$ decimal place).\\
\input{circuit/circuit7}

\item The voltage $v(t)$ across the terminals $a$ and $b$ as shown in the figure, is a sinusoidal voltage having a frequency $\omega=100$ radian/s. when the inductor current $i(t)$ is in phase with the voltage $v(t)$, the magnitude of the impedance $Z$(in $\Omega$) seen between the terminals $a$ and $b$ is $\underline{\hspace{2cm}}$  (up to $2$ decimal place).\\
\input{circuit/circuit8}
\end{enumerate}
\end{document}